\huge A Better (One-Line!) Title Here

### 2016-10-19 pets2017-paper/pets2017-paper.tex
re-ordered some paragraphs in the quantitative section.

Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long.

Measure of success is x\% succeeding and taking no longer than average of y minutes. 
}

@@

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=.5\textwidth]{log-messages.png}
%\caption{
%The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
%These log lines were the result of entering in syntactically correct but invalid proxy settings,
%a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
%technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
%}
%\label{fig:warning_log}
%\end{figure}
%
%We believe that the added advice on what to try next on error messages would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment. The old interface warned users on some mistakes (i.e. entering in a syntactically correct but invalid proxy settings) rather than displaying an error message. When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}). To see the log messages, users must click on the button, open up a text editor, and paste the log messages. The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).
%
%That participant was using the new interface and was told that the bridge configuration was the source of the error. The participant heeded the interface's advice to reconfigure the bridge options. But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results. The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.

@@

Only two participants chose to configure a custom bridge. Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result. Appendix~\ref{custom} shows the malformed requests. These two participants failed to connect to the Tor network.

@@

\subsubsection{Active Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

The overall time was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. With correct configurations, the bootstrap process can take up to two minutes.  With incorrect configurations, a lack of error messages on the progress screen caused some users to wait indefinitely.  Logs show that participants spent 58\% of their overall time at the progress screen. Table ~\ref{table:median_time} shows the median percentage of time spent on each screen.

>>>>

Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long. 
}

@@

We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=.5\textwidth]{log-messages.png}
%\caption{
%The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
%These log lines were the result of entering in syntactically correct but invalid proxy settings,
%a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
%technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
%}
%\label{fig:warning_log}
%\end{figure}

%We believe that the added advice on what to try next on error messages would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment. The old interface warned users on some mistakes (i.e. entering in a syntactically correct but invalid proxy settings) rather than displaying an error message. When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}). To see the log messages, users must click on the button, open up a text editor, and paste the log messages. The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).

%The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.

@@

Only two participants chose to configure a custom bridge. Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result. These two participants failed to connect to the Tor network.

@@

\subsubsection{Active Time to Success} 
The overall time was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. With correct configurations, the bootstrap process can take up to two minutes.  With incorrect configurations, a lack of error messages on the progress screen caused some users to wait indefinitely.  Logs show that participants spent 58\% of their overall time at the progress screen. Table ~\ref{table:median_time} shows the median percentage of time spent on each screen.
